func-descr.template

### 2025-11-04 reports/capstone-movielens.site/05.appendix.Rmd
Data Helper functions: working...

# Appendix {#appndx_a}
## Common Helper Functions
### Logging Functions {#appndx_a.CHF.logging-funcs}

@@

:::
::: { #func.clamp.args.min .sidebar }
  - **min:** Minimum allowed value;

:::
:::
::: { #func.clamp.args.max .sidebar }
  - **max:** Maximum allowed value;

@@

::: { #func.clamp.details .sidebar }
##### Details
\

As explained in [Section  23.4 *User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings cannot be below 0.5 or above 5. For this reason, we need a function described in that section[@IDS2_23-4]:

Therefore, in our project this function is used to clamp the computed movie rating values between 0.5 and 5.

@@

The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#453) function is shown below:
```{r eval=FALSE}
msg.glue <- function(msg_template, arg, arg.name = "%1"){
  msg_template |>
    msg.set_arg(arg, arg.name) |>
    str_glue()
}
```

@@

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
:::

@@

##### Usage

@@

>>>>

# Appendix A: Support Functions {#appndx_a}
## Common Helper Functions
### Logging Functions {#appndx_a.CHF.logging-funcs}

@@

:::
::: { #func.clamp.args.min .sidebar }
  - **min:** Minimum allowed value (0.5 by default);

:::
:::
::: { #func.clamp.args.max .sidebar }
  - **max:** Maximum allowed value (5 by default);

@@

::: { #func.clamp.details .sidebar }
##### Details
\
As explained in [Section 25.1 *Case study: recommendation systems / User effects*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#user-effects) of the _Course Textbook_ we know ratings cannot be below 0.5 or above 5. For this reason, we need a function described in that section[@IDS2_25-1]:

This function is a wrapper for the [base::pmin](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/Extremes) and [base::pmax](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/Extremes) `R` functions, which are called internally to constrain the input value passed in the [r](#func.clamp.args.r) argument to be within the values passed in the [min](#func.clamp.args.min) and [max](#func.clamp.args.max) arguments, respectively.

In our project this function is used to clamp the computed movie rating values between 0.5 and 5.
:::

@@

The source code of the [msg.glue](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L453) function is shown below:
```{r eval=FALSE}
msg.glue <- function(msg_template, arg, arg.name = "%1"){
  msg_template |>
    msg.set_arg(arg, arg.name) |>
    str_glue()
}
```

@@

### Initializing Input Datasets

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the the [Initializing input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) script on _GitHub_.
:::

#### [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) Function {#func.make_source_datasets}
\

Creates the major input datasets used throughout the project.

::: { #func.make_source_datasets.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
movielens_datasets <- make_source_datasets()

This function produces datasets listed in the [Value](#func.make_source_datasets.value) section below and described in detail in [Appendix B: Model Training Datasets] using the `edx` as the original dataset.

::: { #func.make_source_datasets.value .sidebar }
##### Value
\

The list of the following datasets are returned to the client code:

  - [`edx.mx` Matrix Object];

  - [`edx.sgr` Object];

  - [`movie_map` Object];

  - [`date_days_map` Object];

  - [`edx_CV` Object];

::: { #func.make_source_datasets.code .sidebar }
##### Source Code
\

The pseudocode of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) function is shown below:
```{r eval=FALSE}
make_source_datasets <- function(){

    put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
  edx.mx <- edx |> 
    mutate(userId = factor(userId),
           movieId = factor(movieId)) |>
    select(movieId, userId, rating) |>
    pivot_wider(names_from = movieId, values_from = rating) |>
    column_to_rownames("userId") |>
    as.matrix()

  put_log("Function: `make_source_datasets`:
Matrix created: `edx.mx` of the following dimentions:")
  put(dim(edx.mx))

  #> To be able to map movie IDs to titles we create the following lookup table:
  movie_map <- edx |> select(movieId, title, genres) |> 
    distinct(movieId, .keep_all = TRUE)

  put_log("Function: `make_source_datasets`: Dataset created: movie_map")

  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
  date_days_map <- edx |>
    mutate(date_time = as_datetime(timestamp)) |>
    mutate(date = as_date(date_time)) |>
    mutate(year = year(date_time)) |>
    mutate(days = as.integer(date - min(date))) |>
    select(timestamp, date_time, date, year, days) |>
    distinct(timestamp, .keep_all = TRUE)

  str(date_days_map)
  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")

  put_log("Function: `make_source_datasets`: 
To account for the Movie Genre Effect, we need a dataset with split rows 
for movies belonging to multiple genres.")
  edx.sgr <- splitGenreRows(edx)

  #> We will use K-fold cross validation as explained in 
  #> Section 29.6.1: "K-fold validation" of the Cource Textbook:
  #> https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation
  edx_CV <- lapply(kfold_index, function(fold_i){...}

  list(edx_CV = edx_CV,
       edx.mx = edx.mx,
       edx.sgr = edx.sgr,
       tuning_sets = tuning_sets,
       movie_map = movie_map,
       date_days_map = date_days_map)
}
```

::: {.noteblock data-latex=""}
The complete source code of the [make_source_datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) function is available in the [Initializing input datasets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L88) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L89) script on _GitHub_.
:::
:::

@@

::: { #func.sample_train_validation_sets.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
split_sets <- data |>
      sample_train_validation_sets(seed)
```
:::

::: { #func.sample_train_validation_sets.args .sidebar }
##### Arguments
\

::: { #func.sample_train_validation_sets.args.data .sidebar }
  - **data:** ;

:::
::: { #func.sample_train_validation_sets.args.seed .sidebar }
  - **seed:** ;

::: { #func.sample_train_validation_sets.details .sidebar }
##### Details
\

::: { #func.sample_train_validation_sets.value .sidebar }
##### Value
\

::: { #func.sample_train_validation_sets.code .sidebar }
##### Source Code
\

The source code of the [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) function is shown below:
```{r eval=FALSE}
sample_train_validation_sets <- function(data, seed){
  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
  set.seed(seed)
  validation_ind <- 
    sapply(splitByUser(data),
           function(i) sample(i, ceiling(length(i)*.2))) |> 
    unlist() |> 
    sort()

  put_log("Function: `sample_train_validation_sets`: 
Extracting 80% of the original `data` not used for the Validation Set, 
excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")

  train_set <- data[-validation_ind,]

  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
  put(summary(train_set))

  put_log("Function: `sample_train_validation_sets`: 
To make sure we don’t include movies in the Training Set that should not be there, 
we exclude entries using the semi_join function from the Validation Set.")
  tmp.data <- data[validation_ind,]

  validation_set <- tmp.data |> 
    semi_join(train_set, by = "movieId") |> 
    semi_join(train_set, by = "userId") |>
    as.data.frame()

  # Add rows excluded from `validation_set` into `train_set`
  tmp.excluded <- anti_join(tmp.data, validation_set)
  train_set <- rbind(train_set, tmp.excluded)

  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
  put(summary(validation_set))

  # CV train & test sets Consistency Test
  validation.left_join.Nas <- train_set |>
    mutate(tst.col = rating) |>
    select(userId, movieId, tst.col) |>
    data.consistency.test(validation_set)

  put_log("Function: `sample_train_validation_sets`:
Below are the data consistency verification results")
  put(validation.left_join.Nas)

  # Return result datassets    
  list(train_set = train_set, 
       validation_set = validation_set)
}
```

::: {.noteblock data-latex=""}
The source code of the [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) function is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) script on _GitHub_.
:::
:::

@@

## Model Training: Support Functions
\

### Overal Mean Rating (OMR) Model Functions
\

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R) script on _GitHub_.
:::

#### [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) Function {#func.@@func}
\

::: { #func.@@func.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
@@func()

::: { #func.@@func.args .sidebar }
##### Arguments
\

::: { #func.@@func.args. .sidebar }
  - **x:** ;

::: { #func.@@func.details .sidebar }
##### Details
\

::: { #func.@@func.value .sidebar }
##### Value
\

::: { #func.@@func.code .sidebar }
##### Source Code
\

The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [@@script.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) script on _GitHub_.
:::
:::

# Appendix B: Model Training Datasets {#appndx_b}
\

## `edx.mx` Matrix Object
\

We use the array representation described in [Section 18.5 *Analysis of variance (ANOVA)*](https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova) of the _Course Textbook (New Edition)_, for the training data[@IDS2_18-5]. For this purpose, we will convert the `edx` dataset into a matrix using the `tidyr::pivot_wider` function:

```{r eval=FALSE}

  put_log("Function: `make_source_datasets`: Creating Rating Matrix from `edx` dataset...")
  edx.mx <- edx |> 
    mutate(userId = factor(userId),
           movieId = factor(movieId)) |>
    select(movieId, userId, rating) |>
    pivot_wider(names_from = movieId, values_from = rating) |>
    column_to_rownames("userId") |>
    as.matrix()

  put_log("Function: `make_source_datasets`:
Matrix created: `edx.mx` of the following dimentions:")
  put(dim(edx.mx))
```

```{r}
  str(edx.mx)
```

## `edx.sgr` Object
\

To account for the Movie Genre Effect more accurately, we need a dataset with split rows for movies belonging to multiple genres:
```{r eval=FALSE}
  put_log("Function: `make_source_datasets`: 
To account for the Movie Genre Effect, we need a dataset with split rows 
for movies belonging to multiple genres.")
  edx.sgr <- splitGenreRows(edx)
```
```{r}
str(edx.sgr)
summary(edx.sgr)
```

Note that we use the `splitGenreRows` function to split rows of the original dataset:
```{r eval=FALSE}
splitGenreRows <- function(data){
  put("Splitting dataset rows related to multiple genres...")
  start <- put_start_date()
  gs_splitted <- data |>
    separate_rows(genres, sep = "\\|")
  put("Dataset rows related to multiple genres have been splitted to have single genre per row.")
  put_end_date(start)
  gs_splitted
}
```

::: {.noteblock data-latex=""}
The [source code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L73) of the function mentioned above is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R) script on _GitHub_.
:::

## `movie_map` Object
\

To be able to map movie IDs to titles we create the following lookup table:
```{r eval=FALSE}
movie_map <- edx |> select(movieId, title, genres) |> 
    distinct(movieId, .keep_all = TRUE)

  put_log("Function: `make_source_datasets`: Dataset created: movie_map")
```

```{r}
str(movie_map)
summary(movie_map)
```

Note that titles cannot be considered unique, so we cannot use them as IDs[@IDS2_25-1].

## `date_days_map` Object
\

We have a `timestamp` field in the `edx` dataset.
To be able to map the date, year, and number of days since the earliest record in the `edx` dataset with the corresponding value in this field, we create the following lookup table:
```{r eval=FALSE}
  put_log("Function: `make_source_datasets`: Creating Date-Days Map dataset...")
  date_days_map <- edx |>
    mutate(date_time = as_datetime(timestamp)) |>
    mutate(date = as_date(date_time)) |>
    mutate(year = year(date_time)) |>
    mutate(days = as.integer(date - min(date))) |>
    select(timestamp, date_time, date, year, days) |>
    distinct(timestamp, .keep_all = TRUE)

  put_log("Function: `make_source_datasets`: Dataset created: date_days_map")
```
``` {r}
  str(date_days_map)
  summary(date_days_map)
```

## `edx_CV` Object
\

Here we have a list of sample objects we need to perform the _5-Fold Cross Validation_ 
as explained in [Section 31.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_31-6]:
```{r eval=FALSE}
  start <- put_start_date()
  edx_CV <- lapply(kfold_index,  function(fold_i){

    put_log1("Method `make_source_datasets`: 
Creating K-Fold Cross Validation Datasets, Fold %1", fold_i)

    #> We split the initial datasets into training sets, which we will use to build 
    #> and train our models, and validation sets in which we will compute the accuracy 
    #> of our predictions, the way described in the `Section 23.1.1 Movielens data`
    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movielens-data) 
    #> of the Course Textbook.

    split_sets <- edx |>
      sample_train_validation_sets(fold_i*1000)

    train_set <- split_sets$train_set
    validation_set <- split_sets$validation_set

    put_log("Function: `make_source_datasets`: 
Sampling 20% from the split-row version of the `edx` dataset...")
    split_sets.gs <- edx.sgr |>
      sample_train_validation_sets(fold_i*2000)

    train.sgr <- split_sets.gs$train_set
    validation.sgr <- split_sets.gs$validation_set

    # put_log("Function: `make_source_datasets`: Dataset created: validation.sgr")
    # put(summary(validation.sgr))

    #> We will use the array representation described in `Section 17.5 of the Textbook`
    #> (https://rafalab.dfci.harvard.edu/dsbook-part-2/linear-models/treatment-effect-models.html#sec-anova), 
    #> for the training data. 
    #> To create this matrix, we use `tidyr::pivot_wider` function:

    put_log("Function: `make_source_datasets`: Creating Rating Matrix from Train Set...")
    train_mx <- train_set |> 
      mutate(userId = factor(userId),
             movieId = factor(movieId)) |>
      select(movieId, userId, rating) |>
      pivot_wider(names_from = movieId, values_from = rating) |>
      column_to_rownames("userId") |>
      as.matrix()

    put_log("Function: `make_source_datasets`:
Matrix created: `train_mx` of the following dimentions:")
    put(dim(train_mx))

    list(train_set = train_set,
         train_mx = train_mx,
         train.sgr = train.sgr,
         validation_set = validation_set)
  })
  put_end_date(start)
  put_log("Function: `make_source_datasets`: 
Set of K-Fold Cross Validation datasets created: edx_CV")
```
```{r}
str(edx_CV)
```

::: {.noteblock data-latex=""}
This code snippet is a [part](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L140) of the [make_source_datasets](#func.make_source_datasets) _function_ code described above.
:::

Note that we used the [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) function call to split the original dataset (`edx` in this case): 
```{r eval=FALSE}
    split_sets <- edx |>
      sample_train_validation_sets(fold_i*1000)
```

which returns a pair of train/validation sets:
```{r eval=FALSE}
sample_train_validation_sets <- function(data, seed){
  put_log("Function: `sample_train_validation_sets`: Sampling 20% of the `data` data...")
  set.seed(seed)
  validation_ind <- 
    sapply(splitByUser(data),
           function(i) sample(i, ceiling(length(i)*.2))) |> 
    unlist() |> 
    sort()

  put_log("Function: `sample_train_validation_sets`: 
Extracting 80% of the original `data` not used for the Validation Set, 
excluding data for users who provided no more than a specified number of ratings: {min_nratings}.")

  train_set <- data[-validation_ind,]

  put_log("Function: `sample_train_validation_sets`: Dataset created: train_set")
  put(summary(train_set))

  put_log("Function: `sample_train_validation_sets`: 
To make sure we don’t include movies in the Training Set that should not be there, 
we exclude entries using the semi_join function from the Validation Set.")
  tmp.data <- data[validation_ind,]

  validation_set <- tmp.data |> 
    semi_join(train_set, by = "movieId") |> 
    semi_join(train_set, by = "userId") |>
    as.data.frame()

  # Add rows excluded from `validation_set` into `train_set`
  tmp.excluded <- anti_join(tmp.data, validation_set)
  train_set <- rbind(train_set, tmp.excluded)

  put_log("Function: `sample_train_validation_sets`: Dataset created: validation_set")
  put(summary(validation_set))

  # CV train & test sets Consistency Test
  validation.left_join.Nas <- train_set |>
    mutate(tst.col = rating) |>
    select(userId, movieId, tst.col) |>
    data.consistency.test(validation_set)

  put_log("Function: `sample_train_validation_sets`:
Below are the data consistency verification results")
  put(validation.left_join.Nas)

  # Return result datassets ----------------------------------------------------    
  list(train_set = train_set, 
       validation_set = validation_set)
}

::: {.noteblock data-latex=""}
The [sample_train_validation_sets](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L17) function is defined in the same script as the [make_source_datasets](#func.make_source_datasets), from which it is called.
:::

# End of Report -------------------------------------------------------------

### 2025-11-04 reports/capstone-movielens.site/work/func-descr.template.Rmd
Data Helper functions: working...

#### [dat-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) Function {#func.dat-func.tmpl}
\

::: { #func.dat-func.tmpl.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
dat-func.tmpl()

@@

::: { #func.dat-func.tmpl.args .sidebar }
##### Arguments
\

::: { #func.dat-func.tmpl.args. .sidebar }
  - **:** ;

:::
::: { #func.dat-func.tmpl.args. .sidebar }
  - **:** ;

@@

::: { #func.dat-func.tmpl.details .sidebar }
##### Details
\

@@

::: { #func.dat-func.tmpl.value .sidebar }
##### Value
\

@@

::: { #func.dat-func.tmpl.code .sidebar }
##### Source Code
\

The source code of the [dat-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [dat-func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) script on _GitHub_.
:::
:::

>>>>

## Data Helper Functions
\
#### [dat_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) Function {#func.dat_func.tmpl}
\

::: { #func.dat_func.tmpl.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
dat_func.tmpl()

@@

::: { #func.dat_func.tmpl.args .sidebar }
##### Arguments
\

::: { #func.dat_func.tmpl.args. .sidebar }
  - **:** ;

:::
::: { #func.dat_func.tmpl.args. .sidebar }
  - **:** ;

@@

::: { #func.dat_func.tmpl.details .sidebar }
##### Details
\

@@

::: { #func.dat_func.tmpl.value .sidebar }
##### Value
\

@@

::: { #func.dat_func.tmpl.code .sidebar }
##### Source Code
\

The source code of the [dat_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [dat_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) script on _GitHub_.
:::
:::

### Data processing function
\

#### [datproc_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) Function {#func.datproc_func.tmpl}
\

::: { #func.datproc_func.tmpl.Usage .sidebar }
##### Usage
\

::: { #func.datproc_func.tmpl.args .sidebar }
##### Arguments
\

::: { #func.datproc_func.tmpl.args.data .sidebar }
  - **data:** ;

:::
::: { #func.datproc_func.tmpl.args.seed .sidebar }
  - **seed:** ;

::: { #func.datproc_func.tmpl.details .sidebar }
##### Details
\

::: { #func.datproc_func.tmpl.value .sidebar }
##### Value
\

::: { #func.datproc_func.tmpl.code .sidebar }
##### Source Code
\

The source code of the [datproc_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [datproc_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) script on _GitHub_.
:::
:::
